Combining living and fossil taxa into phylogenies: the missing data issue

### 2015-01-09 Manuscript/TEM_draft.tex
Removed comments and added last §

%Removed figure (table instead)
%\begin{figure} 
%\centering
  %  \includegraphics[width=1\textwidth]{Figures/In_main/BC-MethodComp-RF+Tr-colour.pdf}
%\caption{Distribution of the Bhattacharyya Coefficients between methods. Curves represents the kernel density estimations of the Bhattacharyya Coefficients between the four different methods. A. Results for the Normalised Robinson-Foulds distance. B. Results with the for Normalised Triplets distance. Pikes around the two different extremes values of the Bhattacharyya Coefficients show the two pairs of most dissimilar methods (Bayesian consensus vs. Bootstraps and Bayesian consensus vs. Bayesian posterior trees) for the Normalised Robinson-Foulds distance ; and the most similar methods (Bootstraps and Bayesian posterior trees) for the Normalised Triples methods.}
%\label{Fig_Results-paircomp_without} %Comparisons between methods, both in RF and Triplets.(method differences)
%\end{figure}

@@

% Another practical implication of our results regards the tree building methods. Bayesian = better if chooisng one tree as backbone. However, although posterior distributions perform poorly this is more an effect of the way we compare trees (see above). Thus we do not suggest discarding posterior distribution. They are useful for comparative analyses and stuff.

>>>>

@@

Another practical implication of our results regards the tree inference methods and their ability to recover the "best" tree topology with missing data in a Total Evidence framework. Because the Bayesian consensus tree consistently recovered topologies closer to the "best" tree topology than any other methods, we advice to choose this tree topology as a fixed topology for any further step in tree inference analysis such as Tip-dating \citep{BEASTmaster}. However, although the posterior distribution tree distribution performed poorly in recovering the "best" tree topology, this is more an effect of a caveat in our methods (sse discussion above). %add link
Thus, we do not suggest discarding the Bayesian posterior tree distribution once the topology has been fixed since they can be useful for further comparative analysis \citep[e.g.][]{}. %Bayesian PCM cite
